### 2018-04-05 concepts.tex
small edit

A costly but effective solution is to make $N$ large in comparison to
the number of expected predicate evaluations performed during
delta-debugging.  If the error rate is low enough, the problem
disappears.  However, given the large number of evaluations performed,
this will tend to make delta-debugging extremely slow.  We propose
using a dynamic sampling approach, where $N$ is small, but if the
predicate evaluates to true, $M$ repeated true evaluations
(``replications'') are
required before the predicate returns ``true'' to the delta-debugging
algorithm.  A set of $M$ repeated false positives with
$\frac{N}{M}$ samples each is much less likely than a false positive
with $N$ samples; so long as we accept the resulting bias in favor of
false negatives, we can therefore produce a reduced test with a
desired $P(fail)$ much more cheaply:  the use of replications not only
means we only pay the full sampling price on rare occasions, but a
desired accuracy for $P$ can be obtained with a much smaller value $M
\times N$ than a non-dynamically-sampled $N$.  For example, if we the predicate
is $P(fail) \geq 0.5$, and the true probability for a candidate test
is 0.25, using $N=8$ will give a false positive rate of over 10\%.
Using 4 replications on just 2 samples ($M=4;N=2$) yields a false
positive rate of about 3.7\%, yet requires almost 60\% fewer
executions of the test\footnote{The probability calculations for such comparisons
  are relatively simple, but in real testing are
  usually not very useful, since the true
  probabilitiy distributions of test behaviors vary widely and
  dynamically during the
  delta-debugging process, making exact calculation unwieldy, even if
  the changing probabilities were known; exact results would be based on fictional
  probabilities, so gathering experimental data during a trial
  delta-debugging run and tuning $N$ and $M$ to yield desired
  results is  more effective.}.

>>>>

A costly but effective solution is to make $N$ large in comparison to
the number of expected predicate evaluations performed during
delta-debugging.  If the error rate is low enough, the problem
disappears.  However, given the large number of evaluations performed,
this will tend to make delta-debugging extremely slow.  We propose
using a dynamic sampling approach, where $N$ is small, but if the
predicate evaluates to true, $M$ repeated true evaluations
(``replications'', where the first true evaluation is counted as 1 replication) are
required before the predicate returns ``true'' to the delta-debugging
algorithm.  A set of $M$ repeated false positives with
$\frac{N}{M}$ samples each is much less likely than a false positive
with $N$ samples; so long as we accept the resulting bias in favor of
false negatives, we can therefore produce a reduced test with a
desired $P(fail)$ much more cheaply:  the use of replications not only
means we only pay the full sampling price on rare occasions, but a
desired accuracy for $P$ can be obtained with a much smaller value $M
\times N$ than a non-dynamically-sampled $N$.  For example, if we the predicate
is $P(fail) \geq 0.5$, and the true probability for a candidate test
is 0.25, using $N=8$ will give a false positive rate of over 10\%.
Using 4 replications on just 2 samples ($M=4;N=2$) yields a false
positive rate of about 3.7\%, yet requires almost 60\% fewer
executions of the test\footnote{The probability calculations for such comparisons
  are relatively simple, but in real testing are
  usually not very useful, since the true
  probabilitiy distributions of test behaviors vary widely and
  dynamically during the
  delta-debugging process, making exact calculation unwieldy, even if
  the changing probabilities were known; exact results would be based on fictional
  probabilities, so gathering experimental data during a trial
  delta-debugging run and tuning $N$ and $M$ to yield desired
  results is  more effective.}.
